Eagle: multi-locus association mapping on a genome-wide scale made routine

### 2019-08-19 BIOINF-2019-0261-RevisionV2/supmaterials.tex
still tring to get bioinformatics in the right latex format

\begin{figure}
\caption{Power verse false discovery rates for Eagle and the multi-locus methods. Plots for only those simulation 
scenarios where all multi-locus methods could be implemented are shown.  Eagle has the highest power across the four 
scenarios but MLMM also performs well. A false discovery rate of greater than 10\% is typically not employed in GWASs so the 
upper limit of the x-axis is 0.1.}
\label{supfigpowermultiple}
\begin{center}
\includegraphics[width=15cm, height=15cm]{power1main.eps}
\end{center}

@@

\begin{table}[h]
\scriptsize
\caption{New SNP-trait associations found from the analysis of the mouse data with Eagle.  Due to many of the traits in the study 
being correlated, genetically,  these new findings could be confirmed through their prior discovery with other traits in the original 
mouse study (Prior Associations). }
\label{suptabnew}
\vspace{0.5cm}
\begin{tabular}{lcccp{6cm}}  \hline
     & \multicolumn{3}{c}{New SNP-trait Association}  &  \\  \cline{2-4}
Method           &  Trait  & Chrm  &  Position (Mb)  & \hfil Prior Associations  \\  \hline  
Eagle$^{alt}$  & Bioch.HDL   & 6   & 17.53         & Muscles.Sol.g Muscles.TA.g Muscles.Plant.g Muscles.EDL.g  Muscles.Gast.g 
     SPPI.ln.pa Bioch.Calcium    Bioch.Tot.Cholesterol Bioch.Tot.Protein Bioch.Albumin \\ 
                       & Bioch.LDL   & 6    &  17.53        & Muscles.Sol.g Muscles.TA.g Muscles.Plant.g Muscles.EDL.g  Muscles.Gast.g SPPI.ln.pa Bioch.Calcium  Bioch.Tot.Cholesterol Bioch.Tot.Protein Bioch.Albumin \\  
 Eagle$^{optimal}$  &        Bioch.Tot.Cholesterol  & 4      &  134.58  & FACS.CD3posCD44posCD4CD8Ratio  \\
                        & Bioch.HDL                  & 4      &  134.58  & FACS.CD3posCD44posCD4CD8Ratio   \\
                        &                                    & 6      &    17.53   & Muscles.Sol.g Muscles.TA.g Muscles.Plant.g Muscles.EDL.g  Muscles.Gast.g 
     SPPI.ln.pa Bioch.Calcium    Bioch.Tot.Cholesterol Bioch.Tot.Protein Bioch.Albumin  \\
                        & BMC.Mean                 & 15    &     86.57  & BMC.Median \\
                        & BMC.Mean.N             &  5     &     24.64   &  BMC.Mean BMC.StdDev BMC.StdDev.N  BMC.Max.N  BMC.Median BMC.Kurt
                        BMC.Max BMC.Kurt.N  \\
                        & BMC.Max.N               & 15    &      86.57  & BMC.Median \\
                        & Bioch.LDL                  & 6      &   17.53   & Muscles.Sol.g Muscles.TA.g Muscles.Plant.g Muscles.EDL.g  Muscles.Gast.g 
     SPPI.ln.pa Bioch.Calcium    Bioch.Tot.Cholesterol Bioch.Tot.Protein Bioch.Albumin  \\  \hline

@@

\begin{figure}
\caption{Manhattan plots of the single-locus analysis of the mouse data with FaST-LMM. 
Genome-wide significance thresholds for FaST-LMM were calculated, via the Bonferroni correction 
(pink horizontal line) and permutation (blue horizontal line), at a 5\% significance level. 
}
\label{supmanhattan}
\begin{center}
\includegraphics[width=15cm, height=15cm]{1.jpeg}
\end{center}
\end{figure}

>>>>

\begin{figure}
\caption{Power verse false positive rates for Eagle and the multi-locus methods. Plots for only those simulation 
scenarios where all multi-locus methods could be implemented are shown.  Eagle has the highest power across the four 
scenarios but MLMM also performs well. A false posirive rate of greater than 10\% is typically not employed in GWASs so the 
upper limit of the x-axis is 0.1.}
\label{supfigpowermultiple}
\begin{center}
\includegraphics[width=15cm, height=15cm]{power1main.eps}
\end{center}

@@

\begin{table}[h]
\scriptsize
\caption{New SNP-trait associations found from the analysis of the mouse data with Eagle.  Due to many of the traits in the study 
being correlated, genetically,  these new findings could be confirmed through their prior discovery with other traits in the original 
mouse study (Prior Associations). }
\label{suptabnew}
\vspace{0.5cm}
\begin{tabular}{lcccp{6cm}}  \hline
     & \multicolumn{3}{c}{New SNP-trait Association}  &  \\  \cline{2-4}
Method           &  Trait  & Chrm  &  Position (Mb)  & \hfil Prior Associations  \\  \hline  
Eagle$^{alt}$  & Bioch.HDL   & 6   & 17.53         & Muscles.Sol.g Muscles.TA.g Muscles.Plant.g Muscles.EDL.g  Muscles.Gast.g 
     SPPI.ln.pa Bioch.Calcium    Bioch.Tot.Cholesterol Bioch.Tot.Protein Bioch.Albumin \\ 
                       & Bioch.LDL   & 6    &  17.53        & Muscles.Sol.g Muscles.TA.g Muscles.Plant.g Muscles.EDL.g  Muscles.Gast.g SPPI.ln.pa Bioch.Calcium  Bioch.Tot.Cholesterol Bioch.Tot.Protein Bioch.Albumin \\  
 Eagle$^{optimal}$  &        Bioch.Tot.Cholesterol  & 4      &  134.58  & FACS.CD3posCD44posCD4CD8Ratio  \\
                        & Bioch.HDL                  & 4      &  134.58  & FACS.CD3posCD44posCD4CD8Ratio   \\
                        & Bioch.HDL                                   & 6      &    17.53   & Muscles.Sol.g Muscles.TA.g Muscles.Plant.g Muscles.EDL.g  Muscles.Gast.g 
     SPPI.ln.pa Bioch.Calcium    Bioch.Tot.Cholesterol Bioch.Tot.Protein Bioch.Albumin  \\
                        & BMC.Mean                 & 15    &     86.57  & BMC.Median \\
                        & BMC.Mean.N             &  5     &     24.64   &  BMC.Mean BMC.StdDev BMC.StdDev.N  BMC.Max.N  BMC.Median BMC.Kurt
                        BMC.Max BMC.Kurt.N  \\
                        & BMC.Max.N               & 15    &      86.57  & BMC.Median \\
                        & Bioch.LDL                  & 6      &   17.53   & Muscles.Sol.g Muscles.TA.g Muscles.Plant.g Muscles.EDL.g  Muscles.Gast.g 
     SPPI.ln.pa Bioch.Calcium    Bioch.Tot.Cholesterol Bioch.Tot.Protein Bioch.Albumin  \\  \hline

@@

\begin{figure}
\caption{Manhattan plots of the single-locus analysis of the mouse data with FaST-LMM. 
Genome-wide significance thresholds for FaST-LMM were calculated, via the Bonferroni correction 
(pink horizontal line) and permutation (purple horizontal line), at a 5\% significance level. 
}
\label{supmanhattan}
\begin{center}
\includegraphics[width=15cm, height=15cm]{1.jpeg}
\end{center}
\end{figure}
